\documentclass[12pt,courier]{navymemo}

\usepackage{DEsignature}

\author{Dennis Evangelista}
\title{Character witness for MIDN 2/C Long}
\navysubj{Character witness for MIDN 2/C Long}
%\navyfiling{1530}
%\navyserial{16-0001}
\date{\today}
%\navymarking{UNCLASSIFIED}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Asst Prof Evangelista}
\navyto{Deputy Commandant, CAPT Mathewson, USN}
%\navynumberedvia{Admin officer}
%\navynumberedvia{Executive officer}
%\navyskip{}%
\navysubjline{}%
%\navyskip{}%
%\navyref{refa}{SECNAVINST 5216.5D}
%\navyskip{}%
%\navyencl{encla}{Standard Naval Memo/Letter Examples}
\end{navyletterheader}

\section{Recommendation} I am providing this as a written character reference for MIDN 2/C Scott Long. Mr Long was a student in my sections of ES200 (Introduction to Systems Engineering) and EW202 (Principles of Mechatronics). I recommend retention.  

\section{Discussion} 
\subsection{} Mr Long earned an A in ES200 and a B in EW202. He was a decent student, working well with classmates on several teams. Long was always respectful, polite, and attentive in class. His team's ES200 video game, based on a popular animated series, was outstanding; he also worked well in teams for EW202 labs and the autonomous robot final project. I recall he brought good spirit and a positive attitude to both classes. 

\subsection{} I understand he is in trouble for having alcohol in Bancroft. I was formerly a Navy lieutenant responsible for nuclear matters at Naval Sea Systems Command 08 (Naval Reactors), so I am troubled by anything that calls into question the judgement or integrity of our future officers. In my own experience, I have seen a midshipman who was victim of attempted sexual assault during summer cruise, and I have seen gross cases of lying and willful deletion of files. 

\section{} In the case of Mr Long, based on my own interactions with him, I see a decent person who slipped up and acknowledges his mistake. I recommend he be retained and counseled. Long is of good character and can be salvaged, and I believe he has the potential to grow from this and be a good officer. 

\noclosing 
\includesignature
\signature{D EVANGELISTA}

\copyto
File



%As for the offense, I turned myself in for having alcohol in Bancroft Hall. I am not sure there is much to be able to refute for it but if there is anything at all you could think of would be more than helpful. If you would like to discuss about the offense I would be happy to come by and talk more about it.
%
%Is it helpful if I say along lines of based on my interactions with Mr Long, I believe this is a one time lapse and that he should be retained and counseled... all my interactions with him were positive and I believe he has potential to grow from this and be a good officer etc etc etc something like that? 
%
%I believe what you had before should be sufficient enough. Although I can swear this is a one time lapse, I have heard that the deputy commandant tends to not believe that. I think it may be best to leave that part out, however I’m sure you know much better than I do. I do believe that was Mr. Tamas who put you into the arm lock for 202.

%
%% record note prototype
%\navyrecordnote
%
%\navyrecordnotedistribution{%
%ADM (p)\\
%Rodgers (g)\\
%Kearney (w)}%
%\navyrecordnoteconcurrences{%
%\navyrecordnoteconcurrence{05U}
%\navyrecordnoteconcurrence{05Z}}
%
%
%\navyrecordnotesubjline
%
%\section{}
%The action of this letter is based on a review by Evangelista and comments from Foo and Bar which were resolved or incorporated.
%
%\section{}
%Changes happy to glad. 

\end{document}